\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-28 Writeup/paper.tex
Minor sentence improvement
Improve sentence structure Add UCT ethernet speed

We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.

The Telkom account is a 2 Mbit uncapped account, the rest are 1 GB capped accounts.

@@

The tests were done by doing 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost to the same unpopular video. On the first run (which just happens to be via Telkom) the video is not cached anywhere in South Africa, as a result it has to come from a Google cache in Europe. However, this causes it to get cached so the following runs get served from Telkom's own cache. What we see from WebAfrica in the subsequent run is that the video does not come from Europe or Telkom's cache. It instead comes from a Google cache in South Africa. This means that when we first retrieved the video, it was cached not only to Telkom's servers, but also to Google's South African servers. Both WebAfrica and Cybersmart first serve the video up using Google's South African cache then serve it up using their respective ISP cache. Since Afrihost and Axxess use the same ISP cache as Cybersmart, they are served up directly with the ISP cache in their subsequent runs.

@@

\subsection{UCT Network}
For a comparison, we also ran two tests on the UCT network. The test was run from a laptop connected to the UCT network via Ethernet.

>>>>

We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom. The Telkom account is uncapped while the rest of the accounts are capped at 1 gigabyte.

@@

The tests did 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost to the same unpopular video. On the first run (which just happens to be via Telkom) the video is not cached anywhere in South Africa, as a result it has to come from a Google cache in Europe. However, this causes it to get cached so the following runs get served from Telkom's own cache. What we see from WebAfrica in the subsequent run is that the video does not come from Europe or Telkom's cache. It instead comes from a Google cache in South Africa. This means that when we first retrieved the video, it was cached not only to Telkom's servers, but also to Google's South African servers. Both WebAfrica and Cybersmart first serve the video up using Google's South African cache then serve it up using their respective ISP cache. Since Afrihost and Axxess use the same ISP cache as Cybersmart, they are served up directly with the ISP cache in their subsequent runs.

@@

\subsection{UCT Network}
For a comparison, we also ran two tests on the UCT network. The test was run from a laptop connected to the UCT network via Ethernet running at 100 Mbps.
